Making Soup: Preparing and Validating Models of the Bacterial Cytoplasm for Molecular Simulation

### 2019-11-20 paper/virtual_cytoplasm_v2.tex
Added TOC

Magnesium cations were added to our cytoplasm model as counter-ions
for tRNA and ATP. However, as the simulation progressed, FBP and ATP
aggregated around Mg$^{2+}$ and, by consequence, around tRNA
% {\bf,
%   effectively removing the counter ions from the RNA. IS THAT
%   CORRECT?} {\color{blue} No, Figure \ref{fig:tRNA_aggregation} shows that Mg$^{2+}$ is still concentrated around tRNA in the soup }. 
  After identifying this problem, we used simulations of
small systems containing only the metabolites, Mg$^{2+}$ and water to
test different strategies to prevent aggregation in future studies
using long simulations of cytoplasm models. We found that protonating
the phosphate-containing metabolites is enough to reach this goal
(Fig.~\ref{fig:avoiding_aggregation}). Even though ATPH$_3$ and
FBPH$_4$ are not the biologically relevant forms of these molecules in
physiological pH, using their protonated forms may be an acceptable
compromise between parametrization complexity and practical
results. The biggest impact of this approach is on long range
interactions of these metabolites with other molecules due to the
neutralization of their net charge. However, molecules in a crowded
environment are restrained to smaller volumes and shorter inter
molecular distances, which mitigates the effect of charge
neutralization. It has been suggested that charged species should
employ scaled charges in order to be compatible with the empirical
water models~\cite{Leontyev2009a,Leontyev2011a}. Due to the omission
of the electronic polarization, the screening is underestimated and this
corresponds to applying an effective dielectric constant of about 1.7, alternatively scale the charges down by $\sqrt{1.7}$ which would mean that FBP would get a charge of approximately -3 instead of -4.
Due to the high local
density of negative charges in FBP and ATP this might indeed be an
alternative solution, barring use of polarizable
models~\cite{Ponder2010a,Lopes2013a,Ghahremanpour2018b,Walz2018a}.

@@

% \begin{addendum}
%  \item  
%  \item[Competing Interests] 
%  \item[Correspondence]  
% \end{addendum}

>>>>

Magnesium cations were added to our cytoplasm model as counter-ions
for tRNA and ATP. However, as the simulation progressed, FBP and ATP
aggregated around Mg$^{2+}$ and, by consequence, around tRNA
% {\bf,
%   effectively removing the counter ions from the RNA. IS THAT
%   CORRECT?} {\color{blue} No, Figure \ref{fig:tRNA_aggregation} shows that Mg$^{2+}$ is still concentrated around tRNA in the soup }. 
  After identifying this problem, we used simulations of
small systems containing only the metabolites, Mg$^{2+}$ and water to
test different strategies to prevent aggregation in future studies
using long simulations of cytoplasm models. We found that protonating
the phosphate-containing metabolites is enough to reach this goal
(Fig.~\ref{fig:avoiding_aggregation}). Even though ATPH$_3$ and
FBPH$_4$ are not the biologically relevant forms of these molecules in
physiological pH, using their protonated forms may be an acceptable
compromise between parametrization complexity and practical
results. The biggest impact of this approach is on long range
interactions of these metabolites with other molecules due to the
neutralization of their net charge. However, molecules in a crowded
environment are restrained to smaller volumes and shorter inter
molecular distances, which mitigates the effect of charge
neutralization. It has been suggested that charged species should
employ scaled charges in order to be compatible with the empirical
water models~\cite{Leontyev2009a,Leontyev2011a}. Due to the omission
of the electronic polarization, the screening is underestimated and this
corresponds to applying an effective dielectric constant of about 1.7, alternatively scale the charges down by $\sqrt{1.7}$ which would mean that FBP would get a charge of approximately -3 instead of -4.
Due to the high local
density of negative charges in FBP and ATP this might indeed be an
alternative solution, barring use of polarizable
models~\cite{Ponder2010a,Lopes2013a,Ghahremanpour2018b,Walz2018a,Walz2019b}.

@@

% \begin{addendum}
%  \item  
%  \item[Competing Interests] 
%  \item[Correspondence]  
% \end{addendum}
\subsection*{For Table of Contents Only}
\begin{figure}[htp] 
 \centering
  \includegraphics[height=4.45cm]{soup-toc.pdf}
\end{figure}
